Quality Definitions of Qualities

### 2019-11-20 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated Interoperability and Visibility/Transparency

Definition \ref{InteroperabilitySelected}
rephrased: The effort to exchange information between two or more systems,
products or components and use the information that has been exchanged.

@@

This definition is concise and also detailed enough to show the concept not only
on system, but also on products and components. Rephrased ``degree'' to
``effort'' because the latter is more measurable.

@@

Definition \ref{VisibilitySelected} rephrased: The clarity of documentation for
all of the steps and the current status of a software development process.

>>>>

Definition \ref{InteroperabilitySelected}.

@@

This definition is concise and also detailed enough to show the concept not only
on system, but also on products and components. It also covered the concept with
more than 2 systems.

@@

Definition \ref{VisibilitySelected} rephrased: The extent to which all of the
steps and the current status of a software development process are documented
clearly.
